Maximum Likelihood

### 2017-03-25 sources/Math/MaximumLikelihood.rmd
intro to olavos work

```{R}
A <- -0.25  
B <- -1
AB <- A * B
samples <- rnorm(100000, mean = max$par[1], sd = max$par[2])*rnorm(100000, mean = max$par[1], sd = max$par[2])
h <- hist(samples, freq = FALSE)
h$counts=h$counts/sum(h$counts)
plot(h)
abline(v = AB, lty=2)
```

>>>>

```{R}
A <- -0.25  
B <- -1
AB <- A * B
samples <- rnorm(100000, mean = max$par[1], sd = max$par[2])/max$par[2]*rnorm(100000, mean = max$par[1], sd = max$par[2])/max$par[2]
hist(samples, freq = FALSE, breaks = 50)
abline(v = AB / max$par[2], lty=2)
```
